Intelligent Building Energy Management System

### 2021-04-27 finalReportPres.tex
updated pres

\usepackage{tikz}
% load libraries
\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
\usepackage[siunitx,smartlabels]{circuitikzgit}
\def\smgrid{0.5}
% For compact drawing of resistors and capacitors 1
\ctikzset{resistors/scale=0.5,
  capacitors/scale=0.6,
  sources/scale=0.9} 
\ctikzset{
  amplifiers/fill=cyan,
  sources/fill=green!50,
  diodes/fill=red,
  resistors/fill=violet,
}

@@

\begin{frame}{Introduction}{} % Elliot
    % Applications of Building Energy Management
    % \begin{multicols}{2}
      % \begin{block}{}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item Problems that iBEMS will address
          \begin{itemize}
          \item Can help save on energy costs
          \item Less impact on environment
          \end{itemize}
        \item How can the IoT help?
          \begin{itemize}
          \item WiFi integrated into most buildings
          \item Our Web-based approach simplifies development and end-user experience
          \end{itemize}
        \end{itemize}
      \end{small}
    \end{block}
    \column{0.5\textwidth}
    {\small
      \begin{block}{Overall Goal}
        Overall Goal:
        \begin{itemize}
        \item Create a platform in which users can login and access $2$ or $3$ IoT devices connected to a building's energy supply
        \item Allow user to closely monitor energy usage for residential building
        \end{itemize}
      \end{block}
      }
    \begin{figure}
      \centering
      \includegraphics[scale=0.25]{figs/BEMS_Image.jpg}
      \caption{General BEMS}
      \label{fig:high_level_arch}
    \end{figure}
  \end{columns}

      % \end{block}
    % \end{multicols}
\end{frame}

\section{Architecture}
\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
            \caption{High Level Architecture}
            \label{fig:high_level_arch}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
            \item A microgrid with a smart meter will be simulated in the near future
        \end{itemize}        
    \end{multicols}
\end{frame}

\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{figs/functionalBlockDiagram.pdf}
            \caption{Functional Block Diagram}
            \label{fig:functional_bd}
        \end{figure}

        \begin{small}
            \begin{itemize}
                \item iBEMS receives input from users, connected devices, and will automatically download weather data
                \item The core of iBEMS consists of a web server, a database and software agents which handle interactions with connected devices
                \item Power data, device status, and schedules for each device will be output to the web server. Additionally, connected devices respond to commands from the iBEMS
            \end{itemize}
        \end{small}
    \end{multicols}
\end{frame}

\begin{frame}{Operational Modes}{}
    \begin{enumerate}
        \setcounter{enumi}{-1}
        \item Startup menu
        \item Login - system administrators can add and configure users
        \item Home - view weather data
        \item Controlling devices
        \item Scheduling devices
    \end{enumerate}
\end{frame}

\begin{frame}{System Components}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/overallDiagram.pdf}
        \caption{Interconnection between system components}
        \label{fig:systemComponentInterconnection}
    \end{figure}
\end{frame}

\begin{frame}{Control Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/controlAgentUML.pdf}
        \caption{Control Agent Class Diagram}
        \label{fig:controlAgentClass}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/discoveryAgentUML.pdf}
        \caption{Discovery Agent Class Diagram}
        \label{fig:discoveryAgentClass}
    \end{figure}
\end{frame}

\begin{frame}{Scheduling Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/schedulingAgentUML.pdf}
        \caption{Scheduling Agent Class Diagram}
        \label{fig:schedulingAgentClass}
    \end{figure}
\end{frame}

@@

\section{Embedded/Robotics Computer}
\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/Beaglebone_Receiver_Diagram.png}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

@@

      \draw
      (0,0) to[sqV,invert,l=PWM Signal from embedded computer] ++(0,4*\smgrid)
      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
      to[C,l=$1~{[}\micro\farad{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
      \draw
      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
      \draw
      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\ohm{]}$,-*]++(0,-4*\smgrid)
      to[short]++(-4*\smgrid,0);
      \draw
      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
        Computer ADC (Ground)};
    \end{circuitikz}

    % \begin{figure}
    %     \centering
    %     \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
    %     \caption{Circuit to Measure Power Usage}
    %     \label{fig:Beaglebone_Circuit}
    % \end{figure}
    \begin{itemize}
        \item The embedded computer does not have the ability to measure power, but it does have ADC
        \item Here, the power from the motor driver is being run through a resistor. The ADC reads the voltage across the resistor and since resistance is known, current can be calculated for 1 motor
    \end{itemize}
\end{frame}

@@

        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/connectedSBC.jpg}
            \caption{Embedded Computer Connected}
            \label{fig:connected_bb}
        \end{figure}
    \end{multicols}
    \begin{small}
        \begin{itemize}
            \item Embedded computer accepts control commands and sends data to the server
            \item Red LED indicates the embedded computer is not connected and green LED indicates the embedded computer is connected
        \end{itemize}
    \end{small}
\end{frame}

% \begin{frame}{Frame Title}
%     \begin{figure}
%         \centering
%         \includegraphics{}
%         \caption{Caption}
%         \label{fig:my_label}
%     \end{figure}
% \end{frame}
\section{WeMo Insight Switch}

\begin{frame}{WeMo Insight Switch}{} % Elliot 
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.045]{figs/wemoView.jpg}
            \caption{WeMo Insight Smart Plug}
            \label{fig:wemo}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item Appliance is plugged into the WeMo Switch
            \item WeMo Switch can internally turn power on and off
            \item iBEMS will control the WeMo Switch remotely
        \end{itemize}
    \end{multicols}
\end{frame}

\section{Overall Experimental Setup}
\begin{frame}{Overall Experimental Setup}{} % Elliot 
    \begin{figure}
        \centering
        \includegraphics[scale=0.04]{figs/overallView.jpg}
        \caption{Overall View}
        \label{fig:my_label}
    \end{figure}
    Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis

\end{frame}
\section{Home Page}

\begin{frame}{Startup Menu}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{figs/bemsGUI.png}
            \caption{Desktop GUI}
            \label{fig:desktopgui}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.5]{figs/bemsGUIError.png}
            \caption{Popup Error}
            \label{fig:popuperror}
        \end{figure}
    \end{multicols}
    \begin{itemize}
        \item Clicking "Start iBEMS" will lauch the web server and all 3 agents as well as launch the computer's web browser and load the login page automatically
        \item If the user accidentally clicks "Start iBEMS" while it already running, a warning message will appear to prevent errors
        \item Clicking "Stop iBEMS" will stop the web server and agents and close the web browser
    \end{itemize}
\end{frame}

\begin{frame}{Startup Menu Functions}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/GUI_Diagram.png}
        \caption{Diagram for Startup Menu Functionality}
        \label{fig:GUI_Diagram}
    \end{figure}
\end{frame}

% System Architecture Diagram
\begin{frame}{Home Page}{} % Brian
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.2]{figs/Home_screen.png}
        \caption{Home Screen}
        \label{fig:Home_screen}
    \end{figure}

    \begin{small}
    \begin{itemize}
        \item This will be loaded when iBEMS is first booted and it simply shows some current data about the weather 
        \item The Home Page is also accessible by clicking the Home Icon in the upper left corner
    \end{itemize}
    \end{small}
\end{frame}

\begin{frame}{Active Devices Page}{} % Elliot 
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.13]{figs/ActiveDevices_screen.png}
            \caption{Active Devices Page}
            \label{fig:active_devices}
        \end{figure}
        %\textsc{}
        \begin{itemize}
            \item Page allows users to directly control available devices in real time
            \item WeMo Insight Smart Plug can be turned on and off
            \item PWM duty cycle of the embedded computer can be adjusted in increments of 0.1
        \end{itemize}
    \end{multicols}
\end{frame}

\begin{frame}{WeMo Power Plot}{} % Brian
    \begin{figure}
        \centering
        \includegraphics[scale=0.15]{figs/ActiveDevices_plot.png}
        \caption{Active Devices Plot}
        \label{fig:active_devices_plot}
    \end{figure}

    \begin{small}
        \begin{itemize}
            \item Clicking "View Status Plots" launches modal
            \item User can select any day and view the power usage
        \end{itemize}
    \end{small}
\end{frame}

@@

    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.15]{figs/Applications_screen.png}
            \caption{Scheduling Page}
            \label{fig:schedulingl}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item Clicking on "Applications" on the nav bar loads the weekly scheduling feature
            \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)
        \end{itemize}
    \end{multicols}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}{} % Elliot
  \begin{columns}
    \column{0.5\textwidth}
    \begin{figure}
      \centering
      \includegraphics[scale=0.8]{figs/logo.pdf}
      \label{fig:logo}
    \end{figure}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Advantages: open source, simple interface, modular agent-based code base
      \item Disadvantages: can only operate on a LAN, lacks features of a commercial BEMS system
      \item Challenges: adapting the platform for an enterprise network in a commercial building, security features 
    \end{itemize}
  \end{columns}  
\end{frame}

\begin{frame}
  \begin{block}{Further Improvements}
    \begin{itemize}
    \item Refactor the user interface
    \item Granular user access control
    \item Refactor agent communication
    \item Intelligent algorithms
    \item Mobile app
    \item Persistent device information storage
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\usepackage{tikz}
% load libraries
\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
\usepackage[siunitx,smartlabels]{circuitikz}
\def\smgrid{0.5}
% For compact drawing of resistors and capacitors 1
\ctikzset{resistors/scale=0.5,
  capacitors/scale=0.6,
  sources/scale=0.9} 
\ctikzset{
  amplifiers/fill=cyan,
  sources/fill=green!50,
  diodes/fill=red,
  resistors/fill=violet,
}

@@

\begin{frame}{Introduction}{} % Elliot
    % Applications of Building Energy Management
    % \begin{multicols}{2}
      % \begin{block}{}
  \begin{columns}
    \column{0.45\textwidth}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item Problems that iBEMS will address
          \begin{itemize}
          \item Can help save on energy costs
          \item Less impact on environment
          \end{itemize}
        \item How can the IoT help?
          \begin{itemize}
          \item WiFi integrated into most buildings
          \item Our Web-based approach simplifies development and end-user experience
          \end{itemize}
        \end{itemize}
      \end{small}
    \end{block}
    \column{0.5\textwidth}
    {\small
      \begin{block}{Overall Goal}
        \begin{itemize}
        \item Create a platform in which users can login and access $2$ or $3$ IoT devices connected to a building's energy supply
        \item Allow user to closely monitor energy usage for residential building
        \end{itemize}
      \end{block}
      }
    \begin{figure}
      \centering
      \includegraphics[scale=0.25]{figs/BEMS_Image.jpg}
      \caption{General BEMS}
      \label{fig:high_level_arch}
    \end{figure}
  \end{columns}
\end{frame}

\section{Architecture}
\begin{frame}{Architecture}{} % Brian
    \begin{columns}
        \column{0.5\textwidth}
        {\small
        \begin{figure}
            \centering
            \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
            \caption{High Level Architecture}
            \label{fig:high_level_arch}
        \end{figure}
        }
        \column{0.45\textwidth}
        {\small
            \begin{block}{}
                \begin{itemize}
                    \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
                    \item A microgrid with a smart meter could theoretically simulated and connected to by the BEMS core
                \end{itemize}
            \end{block}
        }
    \end{columns}
\end{frame}

\begin{frame}{Architecture}{} % Brian
    \begin{columns}
    \column{0.5\textwidth}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{figs/functionalBlockDiagram.pdf}
            \caption{Functional Block Diagram}
            \label{fig:functional_bd}
        \end{figure}
    \column{0.45\textwidth}
        \begin{block}{}
            \begin{small}
                \begin{itemize}
                    \item iBEMS receives input from users, connected devices, and will automatically download weather data
                    \item The core of iBEMS consists of a web server, a database and software agents which handle interactions with connected devices
                    \item Power data, device status, and schedules for each device will be output to the web server. Additionally, connected devices respond to commands from the iBEMS
                \end{itemize}
            \end{small}
        \end{block}
    \end{columns}
\end{frame}

\begin{frame}{Operational Modes}{}
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/operationalModes.pdf}
        \caption{Operation Modes Interaction}
        \label{fig:functional_bd}
      \end{figure}
    \column{0.45\textwidth}
      \begin{block}{}
        \begin{enumerate}
            \setcounter{enumi}{-1}
            \item Startup menu
            \item Login - system administrators can add and configure users
            \item Home - view weather data
            \item Controlling devices
            \item Scheduling devices
        \end{enumerate}
    \end{block}
    \end{columns}

\end{frame}

\begin{frame}{Agent Communication Architecture}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/overallDiagram.pdf}
        \caption{Interconnection between system components}
        \label{fig:systemComponentInterconnection}
    \end{figure}
\end{frame}

@@

\section{Hardware}
% \section{Embedded/Robotics Computer}

@@

      \draw
      (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
      to[C,l=$1~{[}\micro\farad{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
      \draw
      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
      \draw
      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\ohm{]}$,-*]++(0,-4*\smgrid)
      to[short]++(-4*\smgrid,0);
      \draw
      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
        Computer ADC (Ground)};
    \end{circuitikz}

    \begin{block}{}
      \begin{itemize}
        \item The embedded computer does not have the ability to measure power, but it does have ADC
        \item Here, the power from the motor driver is being run through a resistor. The ADC reads the voltage across the resistor and since resistance is known, current can be calculated for 1 motor
      \end{itemize}
    \end{block}
\end{frame}

@@

        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/connectedSBC.jpg}
            \caption{Embedded Computer Connected}
            \label{fig:connected_bb}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Embedded computer accepts control commands and sends data to the server
            \item Red LED indicates the embedded computer is not connected and green LED indicates the embedded computer is connected
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{WeMo Insight Switch}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \centering
        \includegraphics[scale=0.045]{figs/wemoView.jpg}
        \caption{WeMo Insight Smart Plug}
        \label{fig:wemo}
      \end{figure}
    \column{0.4\textwidth}
     \begin{block}{}
        \begin{itemize}
            \item Appliance is plugged into the WeMo Switch
            \item WeMo Switch can internally turn power on and off
            \item iBEMS will control the WeMo Switch remotely
        \end{itemize}
     \end{block}
    \end{columns}
\end{frame}

% \section{Overall Experimental Setup}
\begin{frame}{Overall Experimental Setup}{} % Elliot 
    \begin{figure}
        \centering
        \includegraphics[scale=0.04]{figs/overallView.jpg}
        \caption{Overall View}
        \label{fig:my_label}
    \end{figure}
    \begin{block}{}
      Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis
    \end{block}
\end{frame}

\section{Software Implementation}

\begin{frame}{Control Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/periodicQueryBehaviorFlow.pdf}
        \caption{periodicQueryBehavior Flow Chart}
        \label{fig:periodicQueryBehavior}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/setDeviceToActiveFlow.pdf}
        \caption{setDeviceToActive Flow Chart}
        \label{fig:setDeviceToActive}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/searchForDevicesFlow.pdf}
        \caption{searchForDevices Flow Chart}
        \label{fig:searchForDevices}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.30]{figs/Beaglebone_Receiver_Diagram.pdf}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Startup Menu}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.2]{figs/BEMS_GUI_Linux.png}
            \caption{Desktop GUI}
            \label{fig:desktopgui}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.35]{figs/BEMS_GUI_Linux_Warning.png}
            \caption{Popup Error}
            \label{fig:popuperror}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{itemize}
        \item Clicking "Start iBEMS" will lauch the web server and all 3 agents as well as launch the computer's web browser and load the login page automatically
        \item If the user accidentally clicks "Start iBEMS" while it already running, a warning message will appear to prevent errors
        \item Clicking "Stop iBEMS" will stop the web server and agents and close the web browser
    \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Startup Menu Functions}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/GUI_Diagram.pdf}
        \caption{Diagram for Startup Menu Functionality}
        \label{fig:GUI_Diagram}
    \end{figure}
\end{frame}

% System Architecture Diagram
\begin{frame}{Home Page}{} % Brian
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.2]{figs/Home_screen.png}
        \caption{Home Screen}
        \label{fig:Home_screen}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item This will be loaded when iBEMS is first booted and it simply shows some current data about the weather 
        \item The Home Page is also accessible by clicking the Home Icon in the upper left corner
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{Active Devices Page}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.13]{figs/ActiveDevices_screen.png}
            \caption{Active Devices Page}
            \label{fig:active_devices}
        \end{figure}
    \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Page allows users to directly control available devices in real time
            \item WeMo Insight Smart Plug can be turned on and off
            \item PWM duty cycle of the embedded computer can be adjusted in increments of 0.1
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}

\begin{frame}{WeMo Power Plot}{} % Brian
    \begin{figure}
        \centering
        \includegraphics[scale=0.15]{figs/ActiveDevices_plot.png}
        \caption{Active Devices Plot}
        \label{fig:active_devices_plot}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Clicking "View Status Plots" launches modal
            \item User can select any day and view the power usage
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

@@

    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.15]{figs/Applications_screen.png}
            \caption{Scheduling Page}
            \label{fig:schedulingl}
        \end{figure}
        \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Clicking on "Applications" on the nav bar loads the weekly scheduling feature
            \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}{} % Elliot
  \begin{columns}
    \column{0.5\textwidth}
    \begin{figure}
      \centering
      \includegraphics[scale=0.8]{figs/logo.pdf}
      \label{fig:logo}
    \end{figure}
    \column{0.45\textwidth}
    \begin{block}{}
      \begin{itemize}
      \item Advantages: open source, simple interface, modular agent-based code base
      \item Disadvantages: can only operate on a LAN, lacks features of a commercial BEMS system
      \item Challenges: adapting the platform for an enterprise network in a commercial building, security features 
    \end{itemize}
    \end{block}
  \end{columns}  
\end{frame}

\begin{frame}{Conclusion}{}
  \begin{block}{Further Improvements}
    \begin{itemize}
    \item Refactor the user interface
    \item Granular user access control
    \item Refactor agent communication
    \item Intelligent algorithms
    \item Mobile app
    \item Persistent device information storage
    \end{itemize}
  \end{block}
\end{frame}
